Figure 1-Supplement 1b

### 2017-12-09 inst/tcga_correlation_table/tcga_correlation_table.Rmd
all paths updated to match article inc. Rmd titles

---
title: "Supplementary Figure 1a"
subtitle: "TCGA correlation table"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r, warning = FALSE}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1a"][[1]])
# pdf(file = path, width = 14)
# gridExtra::grid.table(table, rows = NULL)
# invisible(dev.off())
```

>>>>

---
title: "Figure 1-Supplement 1a"
subtitle: "TCGA correlation table"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r, warning = FALSE}
url <- fileMap(type = "rds")["Figure 1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1a"][[1]])
# pdf(file = path, width = 14)
# gridExtra::grid.table(table, rows = NULL)
# invisible(dev.off())
```

### 2017-12-09 inst/tcga_expression/tcga_expression.Rmd
all paths updated to match article inc. Rmd titles

---
title: "Figure 1c"
subtitle: "miR34a asRNA and miR34a TCGA correlation"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

#calculate stats
stats <- data %>%
  group_by(cancer_PAM50, gene, TP53) %>%
  summarize(value = list(value)) %>%
  spread(TP53, value) %>%
  mutate(
    mean_wt = mean(unlist(`TP53 wt`)),
    mean_mut = mean(unlist(`TP53 mut`)),
    CI95l_wt = t.test(unlist(`TP53 wt`))$conf.int[1],
    CI95l_mut = t.test(unlist(`TP53 mut`))$conf.int[1],
    CI95h_wt = t.test(unlist(`TP53 wt`))$conf.int[2],
    CI95h_mut = t.test(unlist(`TP53 mut`))$conf.int[2],
    pValue = t.test(unlist(`TP53 wt`), unlist(`TP53 mut`))$p.value
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer_PAM50:`TP53 wt`), -pValue) %>%
  separate(col = metric, into = c("metric", "TP53"), sep = "_") %>%
  spread(metric, value) %>%
  mutate(TP53 = if_else(TP53 == "wt", "TP53 wt", "TP53 mut")) %>%
  pFormat(.)

@@

```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE}
ggplot(data = NULL) + 
  geom_jitter(
    data = data,
    aes(
      x = cancer_PAM50,
      y = value,
      colour = TP53
    ),
    position = position_dodge(width = 0.75),
    alpha = 0.5
  ) +
  geom_text(
    data = stats, 
    aes(
      x = cancer_PAM50, 
      y = 1, 
      label = pFormat
    )
  ) +
  geom_point(
    data = stats,
    aes(
      x = cancer_PAM50,
      y = mean,
      group = TP53
    ),
    colour = "grey30",
    shape = 124,
    size = 4,
    lwd = 1,
    position = position_dodge(width = 0.75)
  ) +
  facet_wrap(~gene, ncol = 2) +
  coord_flip(ylim = c(-12, 2.05)) +
  labs(
    x = "Cancer",
    y = "Expression"
  ) +
  theme_few() +
  scale_colour_economist() +
  theme(legend.position = "top") +
  guides(colour = guide_legend(title = "TP53 status"))

#plot pdf
figure <- ggplot(data = NULL) + 
  geom_jitter(
    data = data,
    aes(
      x = cancer_PAM50,
      y = value,
      colour = TP53
    ),
    position = position_dodge(width = 0.75),
    alpha = 0.5,
    size = 1
  ) +
  geom_text(
    data = stats, 
    aes(
      x = cancer_PAM50, 
      y = 1, 
      label = pFormat
    ),
    size = 3.25
  ) +
  geom_point(
    data = stats,
    aes(
      x = cancer_PAM50,
      y = mean,
      group = TP53
    ),
    colour = "grey30",
    shape = 124,
    size = 4,
    lwd = 1,
    position = position_dodge(width = 0.75)
  ) +
  facet_wrap(~gene, ncol = 2) +
  coord_flip(ylim = c(-12, 2.05)) +
  labs(
    x = "Cancer",
    y = "Expression"
  ) +
  theme_few() +
  scale_colour_economist() +
  theme(
    plot.margin = unit(rep(0.1, 4), "lines"),
    legend.position = "top",
    legend.background = element_blank(),
    legend.box.spacing = unit(5, "pt"), #this controls the spacing between strip.text.x and the legend
    legend.margin = margin(rep(0, 4), unit = "pt"),
    legend.key.size = unit(1/5, "cm"),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 9),
    axis.title.x = element_text(margin = margin(t = 5)),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.ticks = element_line(size = 0.25),
    axis.ticks.length = unit(1/15, "cm"),
    panel.border = element_rect(fill = NA, size = 0.15)
  ) +
  guides(colour = guide_legend(title = "TP53 status", override.aes = list(size = 3, alpha = 1)))

##save to pdf
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1b"][[1]])
ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 135,
   width = 205,
   units = "mm"
)
```

>>>>

---
title: "Figure 1-Supplement 1b"
subtitle: "miR34a asRNA and miR34a TCGA expression"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

#calculate stats
stats <- data %>%
  group_by(cancer_PAM50, gene, TP53) %>%
  summarize(value = list(value)) %>%
  spread(TP53, value) %>%
  mutate(
    mean_wt = mean(unlist(`TP53 wt`)),
    mean_mut = mean(unlist(`TP53 mut`)),
    CI95l_wt = t.test(unlist(`TP53 wt`))$conf.int[1],
    CI95l_mut = t.test(unlist(`TP53 mut`))$conf.int[1],
    CI95h_wt = t.test(unlist(`TP53 wt`))$conf.int[2],
    CI95h_mut = t.test(unlist(`TP53 mut`))$conf.int[2],
    pValue = wilcox.test(unlist(`TP53 wt`), unlist(`TP53 mut`), alternative = "two.sided")$p.value
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer_PAM50:`TP53 wt`), -pValue) %>%
  separate(col = metric, into = c("metric", "TP53"), sep = "_") %>%
  spread(metric, value) %>%
  mutate(TP53 = if_else(TP53 == "wt", "TP53 wt", "TP53 mut")) %>%
  pFormat(.)

@@

```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE, warning = FALSE}
ggplot(data = NULL) + 
  geom_jitter(
    data = data,
    aes(
      x = cancer_PAM50,
      y = value,
      colour = TP53
    ),
    position = position_dodge(width = 0.75),
    alpha = 0.5
  ) +
  geom_text(
    data = stats, 
    aes(
      x = cancer_PAM50, 
      y = 1, 
      label = pFormat
    )
  ) +
  geom_point(
    data = stats,
    aes(
      x = cancer_PAM50,
      y = mean,
      group = TP53
    ),
    colour = "grey30",
    shape = 124,
    size = 4,
    lwd = 1,
    position = position_dodge(width = 0.75)
  ) +
  facet_wrap(~gene, ncol = 2) +
  coord_flip(ylim = c(-12, 2.05)) +
  labs(
    x = "Cancer",
    y = "Expression"
  ) +
  theme_few() +
  scale_colour_economist() +
  theme(legend.position = "top") +
  guides(colour = guide_legend(title = "TP53 status"))

#plot pdf
figure <- ggplot(data = NULL) + 
  geom_jitter(
    data = data,
    aes(
      x = cancer_PAM50,
      y = value,
      colour = TP53
    ),
    position = position_dodge(width = 0.75),
    alpha = 0.5,
    size = 1
  ) +
  geom_text(
    data = stats, 
    aes(
      x = cancer_PAM50, 
      y = 1, 
      label = pFormat
    ),
    size = 3.25
  ) +
  geom_point(
    data = stats,
    aes(
      x = cancer_PAM50,
      y = mean,
      group = TP53
    ),
    colour = "grey30",
    shape = 124,
    size = 4,
    lwd = 1,
    position = position_dodge(width = 0.75)
  ) +
  facet_wrap(~gene, ncol = 2) +
  coord_flip(ylim = c(-12, 2.05)) +
  labs(
    x = "Cancer",
    y = "Expression"
  ) +
  theme_few() +
  scale_colour_economist() +
  theme(
    plot.margin = unit(rep(0.1, 4), "lines"),
    legend.position = "top",
    legend.background = element_blank(),
    legend.box.spacing = unit(5, "pt"), #this controls the spacing between strip.text.x and the legend
    legend.margin = margin(rep(0, 4), unit = "pt"),
    legend.key.size = unit(1/5, "cm"),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 9, margin = margin(t = 5)),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.ticks = element_line(size = 0.25),
    axis.ticks.length = unit(1/15, "cm"),
    panel.border = element_rect(fill = NA, size = 0.15)
  ) +
  guides(colour = guide_legend(title = "TP53 status", override.aes = list(size = 3, alpha = 1)))

##save to pdf
# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1b"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 135,
#    width = 205,
#    units = "mm"
# )
```
